### 2015-07-25 paper/paper.Rmd
small things cleanup

Six Things That Affect Education Around the World
========================================================

@@

For each country, average scores on math and reading are calculated separately for boys and girls. These averages are differenced to compute the "gap" between boys and girls. To gauge the statistical significance of the difference, t-statistics and bootstrap confidence intervals were calculated. The results are plotted in the graphs below. Each dot corresponds to a difference between girls' and boys' scores, for each country, with lines giving the confidence interval. Wider intervals indicate less data support the statistics. Color indicates statistical significance (blue in favor of boys, pink in favor of girls, and green means there was no significant difference). The maps color the countries by the presence (or absence) of a gender gap.

@@

# 2. Starting school at an older age generates lower average math scores.

@@

The following R packages were used to conduct the data exploration: shiny, plyr, dplyr, ggplot2, stringr, reshape2, lubridate, maps, ggmap, htmltools, rworldmap, grid, scales, doBy.

>>>>

What Can We Learn About Education Around the World from the PISA Data?
========================================================

@@

For each country, average scores on math and reading are calculated separately for boys and girls. These averages are differenced to compute the "gap" between boys and girls. To gauge the statistical significance of the difference, t-statistics and bootstrap confidence intervals were calculated. The results are plotted in the graphs below. Each dot corresponds to a difference between girls' and boys' scores, for each country, with lines giving the confidence interval. Wider intervals indicate less data support the statistics, for example, Liechtenstein tests few students so there is more uncertainty about the mean. Color indicates statistical significance (blue in favor of boys, pink in favor of girls, and green means there was no difference). The maps color the countries by the presence (or absence) of a gender gap.

@@

# 2. Starting school at an older age is associated with lower average math scores.

@@

The following R packages were used to conduct the data exploration: shiny, plyr, dplyr, ggplot2, stringr, reshape2, lubridate, maps, ggmap, htmltools, rworldmap, grid, scales, doBy. Principles of reproducible research were used for the analysis and the markdown script is available from https://github.com/ijlyttle/isu_pisa/blob/master/paper/paper.Rmd.
